---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(cli.hyperlink = FALSE)
```


## Overview

The tidyomics is a set of packages that work in harmony because they share common data representations and API design, consistent with `tidyverse`. The __tidyomics__ package is designed to make it easy to install and load core packages from the tidyomics in a single command.

If you'd like to learn how to use the tidyomics effectively, the best place to start is [Bioconducotor workshop 2023](https://tidyomics.github.io/tidyomicsWorkshopBioc2023/).

## Installation

::: .pkgdown-devel
```{r eval = FALSE}
# Install from GitHub
remotes::install_github("tidyomics/tidyomics")
```
:::

::: .pkgdown-release

Not yet finalised

```{r eval = FALSE}
BiocManager::install("tidyomics")
```
:::

`library(tidyomics)` will load the core tidyomics packages: 

* [ggplot2](https://ggplot2.tidyomics.org), for data visualisation.
* [dplyr](https://dplyr.tidyomics.org), for data manipulation.
* [tidyr](https://tidyr.tidyomics.org), for data tidying.
* [tidySummarizedExperiment](https://tidySummarizedExperiment.tidyomics.org), for data import.
* [tidySingleCellExperiment](https://tidySingleCellExperiment.tidyomics.org), for functional programming.
* [tidySpatialExperiment](https://tidySingleCellExperiment.tidyomics.org), for functional programming.
* [tidyseurat](https://tidyseurat.tidyomics.org), for tibbles, a modern re-imagining of data frames.
* [plyranges](https://github.com/tidyomics/plyranges), for strings.
* [nullranges](https://github.com/tidyomics/nullranges), for factors.
* [tidybulk](https://github.com/tidyomics/tidybulk), for date/times.

You also get a condensed summary of conflicts (that will decrease as the development progresses) with other packages you have loaded:

```{r example}
library(tidyomics)
```

And you can check that all tidyomics packages are up-to-date with `tidyomics_update()`:

```{r update, eval = FALSE}
tidyomics_update()
#> All tidyomics packages up-to-date
```

## Packages

As well as the core tidyomics, installing this package also installs a selection of other packages that you're likely to use frequently, but probably not in every analysis. This includes packages for:

*   Working with genomic features:

    * [plyranges](https://github.com/tidyomics/plyranges), for strings.
    * [nullranges](https://github.com/tidyomics/nullranges), for factors.
    
*  Working with transcriptomic features:

    * [tidySummarizedExperiment](https://tidySummarizedExperiment.tidyomics.org), for data import.
    * [tidySingleCellExperiment](https://tidySingleCellExperiment.tidyomics.org), for functional programming.
    * [tidySpatialExperiment](https://tidySingleCellExperiment.tidyomics.org), for functional programming.
    * [tidybulk](https://github.com/tidyomics/tidybulk), for date/times.

*   Working with cytometry features:

    * Coming soon...


