---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "# ",
  fig.path = "README-"
)
options(cli.hyperlink = FALSE)
```

## Overview

The [tidyomics](https://github.com/tidyomics) ecosystem is a set of packages for omics data analysis that work together in harmony; they share common Bioconductor data representations and API design consistent with the [tidyverse](https://www.tidyverse.org/) ecosystem. The __tidyomics__ package is designed to make it easy to install and load core packages from the _tidyomics_ ecosystem with a single command.

The core packages are:

```{r, eval = FALSE}
tidyomics_packages()
```

```{r, echo = FALSE}
# Call tidyomics_packages before attaching tidyomics to preserve logical presentation order
tidyomics::tidyomics_packages()
```

## The tidyomics ecosystem 

### Core packages

The core packages are automatically loaded when you run `library(tidyomics)`:

| Package | Intro | GitHub | Description |
|---|---|---|---|
| [tidySummarizedExperiment](https://stemangiola.github.io/tidySummarizedExperiment/) | [Vignette](https://stemangiola.github.io/tidySummarizedExperiment/articles/introduction.html) | [GitHub](https://github.com/stemangiola/tidySummarizedExperiment) | Tidy manipulation of SummarizedExperiment objects |
| [tidySingleCellExperiment](https://stemangiola.github.io/tidySingleCellExperiment) | [Vignette](https://stemangiola.github.io/tidySingleCellExperiment/articles/introduction.html) | [GitHub](https://github.com/stemangiola/tidySingleCellExperiment) | Tidy manipulation of SingleCellExperiment objects |
| [tidySeurat](https://stemangiola.github.io/tidyseurat/) | [Vignette](https://stemangiola.github.io/tidyseurat/articles/introduction.html) | [GitHub](https://github.com/stemangiola/tidyseurat) | Tidy manipulation of Seurat objects |
| [tidySpatialExperiment](https://william-hutchison.github.io/tidySpatialExperiment/) | [Vignette](https://william-hutchison.github.io/tidySpatialExperiment/articles/overview.html) | [GitHub](https://github.com/william-hutchison/tidySpatialExperiment) | Tidy manipulation of SpatialExperiment objects |
| [plyranges](https://sa-lee.github.io/plyranges/) | [Vignette](https://sa-lee.github.io/plyranges/articles/an-introduction.html) | [GitHub](https://github.com/sa-lee/plyranges) | Tidy manipulation of genomics ranges |

### Additional manipulation packages

| Package | Intro | GitHub | Description |
|---|---|---|---|
| [plyinteractions](https://tidyomics.github.io/plyinteractions/) | [Vignette](https://tidyomics.github.io/plyinteractions/articles/plyinteractions.html) | [GitHub](https://github.com/tidyomics/plyinteractions) | Tidy manipulation of genomic interactions |

__plyinteractions__ is under evaluation for inclusion in the core packages in future Bioconductor releases.

### Analysis packages

| Package | Intro | GitHub | Description |
|---|---|---|---|
| [tidybulk](https://stemangiola.github.io/tidybulk/) | [Vignette](https://stemangiola.github.io/tidybulk/articles/introduction.html) | [GitHub](https://github.com/stemangiola/tidybulk/) | Tidy bulk RNA-seq data analysis |
| [nullranges](https://nullranges.github.io/nullranges/) | [Vignette](https://nullranges.github.io/nullranges/articles/nullranges.html) | [GitHub](https://github.com/nullranges/nullranges/) | Generation of null genomic range sets | 

## Installation

Installing the __tidyomics__ package will install all core packages of the _tidyomics_ ecosystem. The __tidyomics__ package can be installed from Bioconductor:

```{r eval = FALSE}
BiocManager::install("tidyomics")
```

Additional packages can be installed independently as needed:

```{r eval = FALSE}
# Additional manipulation package
BiocManager::install("plyinteractions")

# Analysis packages
BiocManager::install("tidybulk")
BiocManager::install("nullranges")
```

## Loading the _tidyomics_ ecosystem

The core _tidyomics_ packages can be attached with:

```{r eval = FALSE}
library(tidyomics)
```

This command also produces a summary of package versions and function conflicts. Function conflicts are a point of ongoing development and will be addressed over time. 

Additional packages can be loaded independently as needed:

```{r eval = FALSE}
# Additional manipulation package
library(plyinteractions)

# Analysis packages
library(tidybulk)
library(nullranges)
```

You are now ready to start using the _tidyomics_ ecosystem.
