---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "# ",
  fig.path = "README-"
)
options(cli.hyperlink = FALSE)
```

## Overview

The [tidyomics](https://github.com/tidyomics)
ecosystem is a set of packages for omics data analysis
that work together in harmony; they share common Bioconductor data
representations and API design, consistent with the
[tidyverse](https://www.tidyverse.org/) ecosystem. 
The __tidyomics__ package is designed to make it easy to install and
load core packages from the _tidyomics_ ecosystem with a single command.

The core packages are:

https://github.com/tidyomics/tidyomics/blob/690945b0ffa23c2b084a66c174fba5696028af87/R/attach.R#L3-L4

## Installation

The __tidyomics__ package can be installed from Github:

```{r eval = FALSE}
remotes::install_github("tidyomics/tidyomics")
```

This will automatically install most packages in the _tidyomics_ ecosystem. The __plyinteractions__, __tidytof__ and __tidySpatialExperiment__ packages are not yet available for automatic installation. For the time being, they can be installed independently: 

```{r eval = FALSE}
BiocManager::install("tidyomics/plyinteractions")
devtools::install_github("keyes-timothy/tidytof")
devtools::install_github("william-hutchison/tidySpatialExperiment")
```

## Loading the _tidyomics_ ecosystem

The core _tidyomics_ packages and supporting _tidyverse_ packages can be loaded with:

```{r eval = FALSE}
library(tidyomics)
```

This command also produces a summary of package versions and function conflicts. Function conflicts are a point of ongoing development and will be addressed over time. 

__plyinteractions__, __tidytof__ and __tidySpatialExperiment__ can be loaded independently:

```{r eval = FALSE}
library(plyinteractions)
library(tidytof)
library(tidySpatialExperiment)
```

You are now ready to start using the _tidyomics_ ecosystem.
