---
title: "Loading the _tidyomics_ ecosystem"
author: "William Hutchison"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
description: > 
  A simple demonstration of installing and loading the tidyomics ecosystem using the tidyomics
  metapackage.
vignette: >
  %\VignetteIndexEntry{Loading the tidyomics ecosystem}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "# "
)
```

## Overview

The [tidyomics](https://github.com/tidyomics) ecosystem is a set of packages for omics data analysis that work together in harmony; they share common Bioconductor data representations and API design consistent with the [tidyverse](https://www.tidyverse.org/) ecosystem. The __tidyomics__ package is designed to make it easy to install and load core packages from the _tidyomics_ ecosystem with a single command.

The core packages are:

https://github.com/tidyomics/tidyomics/blob/690945b0ffa23c2b084a66c174fba5696028af87/R/attach.R#L3-L4

## Installation

The __tidyomics__ package can be installed from GitHub:

```{r eval = FALSE}
remotes::install_github("tidyomics/tidyomics")
```

The __plyinteractions__, __tidySpatialExperiment__ and __tidytof__ packages are not yet available for automatic installation. For the time being, __plyinteractions__ and __tidySpatialExperiment__ can be installed independently: 

```{r eval = FALSE}
BiocManager::install("tidyomics/plyinteractions")
BiocManager::install("william-hutchison/tidySpatialExperiment")
```

And __tidytof__ can be installed via [GitHub](https://github.com/keyes-timothy/tidytof).

## Loading the _tidyomics_ ecosystem

The core _tidyomics_ packages and supporting _tidyverse_ packages can be loaded with:

```{r eval = FALSE}
library(tidyomics)
```

This command also produces a summary of package versions and function conflicts. Function conflicts are a point of ongoing development and will be addressed over time. 

__plyinteractions__, __tidySpatialExperiment__ and __tidytof__ can be loaded independently:

```{r eval = FALSE}
library(plyinteractions)
library(tidySpatialExperiment)
library(tidytof)
```

You are now ready to start using the _tidyomics_ ecosystem.
