---
title: "Loading the _tidyomics_ ecosystem"
author: "William Hutchison"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
description: > 
  A simple demonstration of installing and loading the tidyomics ecosystem using the tidyomics
  metapackage.
vignette: >
  %\VignetteIndexEntry{Loading the tidyomics ecosystem}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "# "
)
```


## Overview

The _tidyomics_ ecosystem is a set of packages for 'omic data analyses that work together in harmony; they share common data representations and API design, consistent with the [_tidyverse_](https://www.tidyverse.org/) ecosystem. The __tidyomics__ package is designed to make it easy to install and load core packages from the _tidyomics_ ecosystem with a single command.

If you would like to learn how to use _tidyomics_ effectively, the best place to start is the [Bioconducotor Workshop 2023](https://tidyomics.github.io/tidyomicsWorkshopBioc2023/).

## Included packages

The _tidyomics_ ecosystem includes packages for:

*   Working with genomic features:

    * [plyranges](https://github.com/sa-lee/plyranges), for tidy manipulation of genomic range data. 
    * [nullranges](https://github.com/nullranges/nullranges), for tidy generation of genomic ranges representing the null hypothesis.
    
*  Working with transcriptomic features:

    * [tidySummarizedExperiment](https://github.com/stemangiola/tidySummarizedExperiment), for tidy manipulation of SummarizedExperiment objects.
    * [tidySingleCellExperiment](https://github.com/stemangiola/tidySingleCellExperiment), for tidy manipulation of SingleCellExperiment objects.
    * [tidySpatialExperiment](https://github.com/william-hutchison/tidySpatialExperiment), for tidy manipulation of SpatialExperiment objects.
    * [tidyseurat](https://github.com/stemangiola/tidyseurat), for tidy manipulation of Seurat objects.
    * [tidybulk](https://github.com/stemangiola/tidybulk), for tidy bulk RNA-seq data analysis.

*   Working with cytometry features:

    * [tidytof](https://github.com/keyes-timothy/tidytof), for tidy manipulation of high-dimensional cytometry data.

## Installation

The __tidyomics__ package can be installed from Github:

```{r eval = FALSE}
remotes::install_github("tidyomics/tidyomics")
```

This will automatically install most packages in the _tidyomics_ ecosystem. The __tidytof__ and __tidySpatialExperiment__ packages are not yet available for automatic installation. For the time being, they can be installed independently: 

```{r eval = FALSE}
devtools::install_github("keyes-timothy/tidytof")
devtools::install_github("william-hutchison/tidySpatialExperiment")
```

## Loading the _tidyomics_ ecosystem

The core _tidyomics_ packages and supporting _tidyverse_ packages can be loaded with:

```{r}
library(tidyomics)
```

This command also produces a summary of package versions and function conflicts. Function conflicts are a point of ongoing development and will be addressed over time. 

__tidytof__ and __tidySpatialExperiment__ can be loaded independently:

```{r eval = FALSE}
library(tidytof)
library(tidySpatialExperiment)
```

You are now ready to start using the _tidyomics_ ecosystem.
